Modeling and analyzing the Corona-virus warning app with the Isabelle Infrastructure framework

### 2020-07-09 paper.tex
renamed ModTrans inot Refeinemnt

The attack tree calculus \cite{kam:18b} exhibits that an attack is possible.
\begin{ttbox}
 corona_Kripke \ttvdash {\sf EF} scorona
\end{ttbox}
We can simply apply the Correctness theorem \texttt{AT\_EF} to 
immediately prove this CTL statement. This application of the meta-theorem 
of Correctness of attack trees saves us proving the CTL formula tediously 
by exploring the state space in Isabelle proofs. Alternatively, we could use 
the generated code for the function \texttt{is\_attack\_tree} in Scala 
(see Section \ref{sec:at}) to check that a refined attack of the above is valid.

>>>>

The attack tree calculus \cite{kam:18b} exhibits that an attack is possible.
\begin{ttbox}
 corona_Kripke \ttvdash {\sf EF} scorona
\end{ttbox}
We can simply apply the Correctness theorem \texttt{AT\_EF} to 
immediately prove this CTL statement. This application of the meta-theorem 
of Correctness of attack trees saves us proving the CTL formula tediously 
by exploring the state space in Isabelle proofs. Alternatively, we could use 
the generated code for the function \texttt{is\_attack\_tree} in Scala 
(see \cite{kam:18b}) to check that a refined attack of the above is valid.
